\documentclass[12pt]{letter}
\usepackage{hyperref}

\begin{document}

\begin{letter}{Physical Review Letters Editorial Office\\
American Physical Society\\
1 Research Road\\
Ridge, NY 11961}

\opening{Dear Editors,}

I am writing to submit our manuscript titled "Love as the Fundamental Force: A Quantum Framework for Consciousness and Universal Coherence" for consideration as an Article in Physical Review Letters.

This work presents a novel theoretical framework that unifies quantum mechanics, consciousness, and universal coherence through the lens of love as a fundamental force. Our key findings include:

\begin{itemize}
\item A mathematical formulation demonstrating love's role in maintaining quantum coherence
\item Experimental validation through detector noise patterns and statistical correlations
\item A predictive framework for consciousness-matter interactions
\item Falsifiable predictions that can be tested in laboratory settings
\end{itemize}

The manuscript includes detailed appendices covering mathematical proofs, experimental methods, and theoretical foundations. Our work bridges multiple disciplines while maintaining rigorous scientific standards and falsifiability.

This research will be of particular interest to the physics community as it:
\begin{itemize}
\item Provides a new perspective on quantum measurement and consciousness
\item Offers experimental protocols for testing consciousness-matter interactions
\item Presents a unified framework for understanding fundamental forces
\item Opens new avenues for quantum consciousness research
\end{itemize}

The manuscript has not been previously published and is not under consideration elsewhere. We have followed all PRL formatting guidelines and included all necessary supplementary materials.

Suggested reviewers:
\begin{itemize}
\item [Names and institutions of 3-4 potential reviewers with expertise in quantum mechanics, consciousness studies, and unified field theories]
\end{itemize}

We believe this work represents a significant advance in our understanding of consciousness, quantum mechanics, and the fundamental nature of reality. We look forward to your response.

\closing{Sincerely,}

[Author Name]\\
[Institution]\\
[Contact Information]

\end{letter}
\end{document} 