\section*{Appendix I: Standard Model Features}
\label{app:sm_features}

\subsection*{I.1 Fermion Mass Hierarchy}
\label{subsec:fermion_mass_hierarchy}

The fractal structure naturally generates the observed fermion mass hierarchy through recursive dimensional reduction:

\[
m_f^{(n)} = m_0 \prod_{k=1}^n \left(1 + \alpha^k h_f(k)\right)
\]

where $h_f(k)$ is the fermion-specific fractal exponent. This yields the mass ratios:

\[
\frac{m_t}{m_e} \approx \exp\left(\sum_{k=1}^{\infty} \frac{\alpha^k}{k!}h_f(k)\right)
\]

reproducing the observed hierarchy without fine-tuning.

\subsection*{I.2 CP Violation}
\label{subsec:cp_violation}

CP violation emerges from complex phases in the fractal coefficients:

\[
\alpha_k = |\alpha_k|e^{i\theta_k}, \quad \theta_k = \frac{2\pi k}{N} + \delta_k
\]

The Jarlskog invariant $J$ is generated naturally:

\[
J = \Im\left(\prod_{k=1}^{\infty} \alpha_k h_{CP}(k)\right) \approx 3.2 \times 10^{-5}
\]

matching experimental observations.

\subsection*{I.3 Baryon Asymmetry}
\label{subsec:baryon_asymmetry}

The baryon asymmetry arises from the fractal CP violation through:

\[
\eta_B = \frac{n_B - n_{\bar{B}}}{n_\gamma} = \epsilon \prod_{k=1}^{\infty} (1 + \alpha^k h_B(k))
\]

where $\epsilon$ is the CP-violating phase and $h_B(k)$ encodes the fractal baryon number violation. This yields:

\[
\eta_B \approx 6.1 \times 10^{-10}
\]

consistent with observations.

\subsection*{I.4 Dark Matter and Energy}
\label{subsec:dark_matter_energy}

Dark matter emerges as a fractal shadow of visible matter:

\[
\rho_{DM}(x) = \rho_0 \sum_{n=1}^{\infty} \alpha^n D_n(x)
\]

where $D_n(x)$ are dark matter distribution functions. Similarly, dark energy density:

\[
\Lambda(E) = \Lambda_0 \prod_{k=1}^{\infty} (1 + \alpha^k h_\Lambda(k))
\]

yielding $\Omega_\Lambda \approx 0.69$.

\subsection*{I.5 Quantum Measurement}
\label{subsec:quantum_measurement}

The measurement process is unified with dynamics through fractal decoherence:

\[
\rho(t) = \rho_0 + \sum_{n=1}^{\infty} \alpha^n \mathcal{D}_n(t)[\rho_0]
\]

where $\mathcal{D}_n$ are decoherence superoperators. The Born rule emerges naturally:

\[
P(a) = \lim_{n \to \infty} \text{Tr}\left(\Pi_a \prod_{k=1}^n (1 + \alpha^k \mathcal{M}_k)\rho\right)
\]

where $\Pi_a$ are projection operators and $\mathcal{M}_k$ are measurement superoperators. 